\Title

### 2021-06-25 manuscript/content.tex
Review the first part of the introduction
Some small wording changes.

Measurements of anomalies in potential fields, like gravity disturbances and
total-field magnetic anomalies, are widely used in geophysical exploration for
their relatively low cost of acquisition.
These data can be surveyed using ground, airborne, shipborne, or satellite
systems.
In ground surveys, the data are often gathered following irregular paths or
networks along the surface of the terrain, leading to highly variable
elevations in mountainous regions.
On airborne surveys, the data are gathered along flight lines, producing a
large number of measurements concentrated along almost straight lines.
Measurement height can also change because of the vertical movement of the
aircraft.
Processing of the data often involves interpolation onto a regular grid at
constant height, both to improve visualization for interpretation purposes as
well as to prepare the data for further processing and modelling (e.g.,
reduction-to-the-pole, derivative calculations, upward continuation, Euler
deconvolution).

Several methods exist in the literature for interpolation in two dimensions,
for example continuous curvature splines in tension \citep{smith1990},
bi-harmonic (thin-plate) splines \citep{sandwell1987}, and kriging \citep{hansen1993}.
These general-purpose methods have limitations when it comes to interpolating
potential field data:
(i)~they are not able to take into account the variable height of the
observation points and
(ii)~the interpolating functions are not necessarily harmonic, which
is the underlying assumption behind many processing techniques
(e.g., upward continuation and vertical derivatives).

A widely used method for interpolating gravity and magnetic data
is the equivalent sources technique (also known as equivalent layer, radial
basis functions, or Green's functions interpolation), first introduced by
\citet{dampney1969}.
It consists in fitting a model of finite elementary sources to the data and
using this model to predict new data values.
Besides interpolation, equivalent sources have been used for
reduction-to-the-pole of magnetic data
\citep{silva1986, nakatsuka2006, guspi2009}, upward
continuation \citep{emilia1973, li2010}, joint processing of gravity gradient
data \citep{barnes2011}, modelling the lithospheric magnetic field
\citep{kother2015}, recovering the magnetic induction vector from
total-field magnetic anomalies \citep{li2020}, and more.

It also worth mentioning the least-squares collocation method
(LSC), which is widely used in geodesy
\citep[][and references therein]{tscherning2015}.
LCS is often applied to combine and interpolate different linear functionals of
the disturbing gravity potential (gravity anomalies, gravity disturbances,
deflections of the vertical, geoid height, et cetera).
Like equivalent sources, collocation also requires the solution of a large
linear system of the order of the number of observed data.
As such, it's practical application suffers from the same computational
challenges.

>>>>

Measurements of anomalies in potential fields, like gravity disturbances and
total-field magnetic anomalies, are widely used in geophysical exploration for
their low cost of acquisition.
These data can be surveyed using ground, airborne, shipborne, or satellite
systems.
During ground surveys, the data are often gathered following irregular paths or
networks along the surface of the terrain, leading to highly variable
elevations in mountainous regions.
Airborne and satellite surveys gather data along flight lines, producing
closely spaced measurements along almost straight lines but with larger spacing
between adjacent lines.
Measurement height can also change because of the vertical movement of the
aircraft.
Processing of the data often involves interpolation onto a regular grid at
constant height, both to improve visualization for interpretation purposes as
well as to prepare the data for further processing and modelling (e.g.,
reduction-to-the-pole, derivative calculations, upward continuation, Euler
deconvolution).

Several methods exist in the literature for interpolation in two dimensions,
for example continuous curvature splines in tension \citep{smith1990},
bi-harmonic (thin-plate) splines \citep{sandwell1987}, and kriging
\citep{hansen1993}.
These general-purpose methods have limitations when it comes to interpolating
potential field data, namely
(i)~they are not able to take into account the variable height of the
observation points and
(ii)~the interpolating functions are not necessarily harmonic, which
is the underlying assumption behind many processing techniques
(e.g., upward continuation and vertical derivatives).

A widely used method for interpolating gravity and magnetic data
is the equivalent sources technique (also known as equivalent layer, radial
basis functions, or Green's functions interpolation).
First introduced by \citet{dampney1969}, the method consists in fitting a model
of finite elementary sources to the data and using this model to predict new
data values.
Besides interpolation, equivalent sources have been used for
reduction-to-the-pole of magnetic data
\citep{silva1986, nakatsuka2006, guspi2009}, upward
continuation \citep{emilia1973, li2010}, joint processing of gravity gradient
data \citep{barnes2011}, modelling the lithospheric magnetic field
\citep{kother2015}, recovering the magnetic induction vector from
total-field magnetic anomalies \citep{li2020}, and more.

It is also worth mentioning the least-squares collocation method
(LSC), which is widely used in geodesy
\citep[][and references therein]{tscherning2015}.
LCS is often applied to combine and interpolate different linear functionals of
the disturbing gravity potential (gravity anomalies, gravity disturbances,
deflections of the vertical, geoid height, et cetera).
Like equivalent sources, collocation also requires the solution of a large
linear system of the order of the number of observed data.
As such, it's practical application suffers from the same computational
challenges.
